Evaluating Perceptual Judgements on 3D Printed Bar Charts

### 2024-01-22 jds.rmd
diff for pdf

```{r demographics, fig.cap="Demographic characteristics of participants in the study.", message=FALSE, warning=FALSE, out.width='100%', fig.width = 9, fig.height = 3.5}
library(patchwork)
valid.users$userAppStartTime <- as.POSIXct(valid.users$userAppStartTime,
           origin = '1970-1-1')

>>>>

```{r demographics, fig.cap="Demographic characteristics of participants in the study.", message=FALSE, warning=FALSE, out.width='100%', fig.width = 9, fig.height = 3.5, cache = F}
library(patchwork)
valid.users$userAppStartTime <- as.POSIXct(valid.users$userAppStartTime,
           origin = '1970-1-1')
